---
title: "Eating Out"
author: "Janette Queazda"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
 Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```



# introduction 

both of the variables we are going to be using is categorical.We will be using eatout out based on race.


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```



In this bar chart in 1996 shows that 80 percent of whites eat out and about a 18 percent of whites do not eat out.Compared to the black race and the other races they eatout less.But overall the black race eatout race.



```{r}
table2 <- xtabs(~eatout + race, data=mydata)
rowPerc(table2)
colPerc(table2)
```
In this this numerical summary shows that that 82.83 percent of white race goes out to eat and 17.17 percent does not eat out.The black people 68.75 percent ate out and 31.25 do not eat out.In the other races 77.78.78 percent eat out and 22.22 percent does not eat out out of 100 percent.



